A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
minor grammar edits

In our model, by separating for state-specific polls, we are able to analyze and model out the poll results by states where state-specific polls were conducted. Examining @fig-state-comparison, common battle ground states such as Arizona, Pennsylvania, Wisconsin and Michigan are polled more frequently at the state-level than partisan states such as California and New York. Examining the results at these key battleground states, the results show that Harris' popularity recenty fell below 50% during October and November in key states such as Arizona, Michigan, Pennsylvania, Nevada and Wisconsin. Though Harris has predicted to have a majority in Ohio and Florida, the disappointing results in the other states make sher lead in these states less signifiant. Moreover, looking at the general NA category,representing all non-state specific polls, Harris' predicted approval rating hovers at 48%, which means she is expected to lose the popular vote to Trump.

@fig-state-summary shows that Harris is projected to have a minor lead with 50.4% of the popular vote in five key states: Virginia, Ohio, New Hampshire, Minnesota, and Florida. However, in the other states, she is expected to lose the popular vote. States such as Pennsylvania, Nevada, Michigan, and Georgia are critical states in order to win the election. As Harris has a noticeable projected minority in these states, she not only is expected to lose the popular vote, but Trump has a projected lead over Harris in these battleground states, hurting her chances at being elected.

Overall, our model predicts that Harris is unlikely to win the general popular vote or key swing states. Consequently, we anticipate Donald Trump will win the 2024 U.S. Presidential election.

>>>>

In our model, by separating for state-specific polls, we are able to analyze and model out the poll results by states where state-specific polls were conducted. Examining @fig-state-comparison, common battle ground states such as Arizona, Pennsylvania, Wisconsin and Michigan are polled more frequently at the state-level than partisan states such as California and New York. Examining the results at these key battleground states, the results show that Harris' popularity recenty fell below 50% during October and November in key states such as Arizona, Michigan, Pennsylvania, Nevada and Wisconsin. Though Harris has predicted to have a majority in Ohio and Florida, the disappointing results in the other states makes her lead in these states less signifiant. Moreover, looking at the general NA category,representing all non-state specific polls, Harris' predicted approval rating hovers at 48%, which means she is expected to lose the popular vote to Trump.

@fig-state-summary shows that Harris is projected to have a minor lead with 50.4% of the popular vote in five key states: Virginia, Ohio, New Hampshire, Minnesota, and Florida. However, in the other states, she is expected to lose the popular vote. Pennsylvania, Nevada, Michigan, and Georgia are critical states for determining the outcome of the election. As Harris has a noticeable projected minority in these states, she not only is expected to lose the popular vote, but Trump has a projected lead over Harris in these battleground states, hurting her chances at being elected.

Thus, our model predicts that Harris is unlikely to win the general popular vote or key swing states. Consequently, we anticipate Donald Trump will win the 2024 U.S. Presidential election.
